Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-24 bbbq_article.tex
Merge

To confirm that peptides stemming from TMHs were presented in MHC-I and MHC-II,
peptide elution studies were reanalyzed.
Table \ref{tab:elution} shows the percentage of epitopes derived 
from a TMH
found in MHC-I and MHC-II elution 
studies (\cite{schellens2015comprehensive} and \cite{bergseng2015different} respectively),
for the two topology prediction tools TMHMM and 
PureseqTM (\cite{krogh2001predicting} and \cite{wang2019efficient} respectively). 
Regardless of the prediction, 
at least 100 epitopes were predicted to be derived from a TMH. 
From these findings, it is robustly predicted that
epitopes derived from TMHs can and are presented on both MHC-I and MHC-II.

>>>>

To confirm that peptides stemming from TMHs were presented in MHC-I and MHC-II,
peptide elution studies were reanalyzed.
Table \ref{tab:elution} shows the percentage of epitopes derived 
from a TMH
found in MHC-I and MHC-II elution 
studies (\cite{schellens2015comprehensive} and \cite{bergseng2015different} respectively),
for the two topology prediction tools TMHMM and 
PureseqTM (\cite{krogh2001predicting} and \cite{wang2019efficient} respectively). 
Regardless of the prediction, 
at least 100 epitopes were predicted to be derived from a TMH. 
From these findings, it is robustly predicted that
epitopes derived from TMHs are presented by B cells [For Frans: please check
that the article by Bergseng, 2015, 'Different binding motifs of the celiac 
disease-associated HLA molecules DQ2. 5, DQ2. 2, and DQ7. 5 revealed by 
relative quantitative proteomics of endogenous peptide repertoires'
is appropriate. As far as I can see, it is, but I may overlook something. Richel].
